\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-06-09 doc/response_2_reviews_Ecography2.txt

Comments to the Author
The manuscript has improved since its previous round. The work is interesting and carefully executed even though authors should be a bit more critical on the generality of their results. After all this is a very theoretical study where the simulation model is rather simplistic description of the reality.

RESPONSE: We re-read the Discussion to make sure we are not over-selling our results. We believe it is clear that our results are based only on simulations of a couple theoretical models, and that empirical tests are still required. Furthermore, the text is littered with qualifying words such as "may", "likely", and "suggest."

Few specific points:
- space-for-time model. I don't understand the motivation behind this term. Moreover, I don't think this is a commonly used term in ecology. I would encourage revising it.

RESPONSE: We responded to this comment in our first revision, pointing out that "a quick search on Google Scholar shows many papers with "space-for-time" in the title or abstract, including papers cited hundreds of times. Stuart Pickett's 1989 book chapter in the Long-term Studies in Ecology, titled, "Space-for-Time Substitution as an Alternative to Long-Term Studies," has been cited almost 1300 times (Google Scholar)."

@@

- On line 254, figures and elsewhere. Please provide units (year?) for time

RESPONSE: We added revised this line, and most figure legends, to clarify that time is measured in years.

### 2020-06-09 doc/manuscript.tex
tiny changes

When we repeated the simulation with a continuous, nonstationary temperature increase, we see a qualitatively similar shift in weights with increasing forecast horizon from the temporal to spatial statistical model (SI Fig. \ref{fig:community-forecast-species-nonstationary}). In this case, the forecast from the temporal statistical model is not as skillful in the near-term forecast horizon, because the model does not account for the temperature trend during the model fitting period. Separating the effect of annual temperature deviations from the temperature trend would distinguish between short and long-term patterns, much as our temporal and spatial statistical models do in the simulation with stationary temperature periods.

@@

With the onset of warming, the population crashed as the cold-adapted genotype decreased in abundance. Eventually, frequencies of the heterozygous genotype and the warm-adapted homozygous genotype began to increase and the population recovered (Fig. \ref{fig:forecast} bottom). The temporal statistical model (solid blue line in Fig. \ref{fig:forecast}) accurately predicted the impact of the initial warming trend, but eventually became too pessimistic, while the spatial statistical model (solid red line in Fig. \ref{fig:forecast}) did not handle the initial trend but accurately predicted the eventual, new steady state (Fig. \ref{fig:forecast} bottom).

As in the community turnover example, we also fit a weighted average of predictions from the spatial and temporal statistical models, with the weights changing over time. This weighted model initially reflected the temporal model (decrease from $t=500$ to $t=600$), but then rapidly transitioned to reflect the spatial model ($t \geq 700$). The rapid transition in the weighting term, $\omega$, occurred during the period of most rapid change in genotype frequencies (Fig. \ref{fig:forecast_supp}). The weighted model's predictions look impressively accurate, but, as in the community turnover example, that is because we used the full, simulated time series to fit the weighting term. A true forecast would require an independent method to predict how the model weights shift over time.

>>>>

When we repeated the simulation with a continuous, nonstationary temperature increase, we see a qualitatively similar shift in weights with increasing forecast horizon from the temporal to spatial statistical model (Fig. \ref{fig:community-forecast-species-nonstationary}). In this case, the forecast from the temporal statistical model is not as skillful in the near-term forecast horizon, because the model does not account for the temperature trend during the model fitting period. Separating the effect of annual temperature deviations from the temperature trend would distinguish between short and long-term patterns, much as our temporal and spatial statistical models do in the simulation with stationary temperature periods.

@@

With the onset of warming, the population crashed as the cold-adapted genotype decreased in abundance. Eventually, frequencies of the heterozygous genotype and the warm-adapted homozygous genotype began to increase and the population recovered (Fig. \ref{fig:forecast} bottom). The temporal statistical model (solid blue line in Fig. \ref{fig:forecast}) accurately predicted the impact of the initial warming trend, but eventually became too pessimistic, while the spatial statistical model (solid red line in Fig. \ref{fig:forecast}) did not handle the initial trend but accurately predicted the eventual, new steady state.

As in the community turnover example, we also fit a weighted average of predictions from the spatial and temporal statistical models (purple line in Fig. \ref{fig:forecast}), with the weights changing over time. This weighted model initially reflected the temporal model (decrease from $t=500$ to $t=600$), but then rapidly transitioned to reflect the spatial model ($t \geq 700$). The rapid transition in the weighting term, $\omega$, occurred during the period of most rapid change in genotype frequencies (Fig. \ref{fig:forecast_supp}). The weighted model's predictions look impressively accurate, but, as in the community turnover example, that is because we used the full, simulated time series to fit the weighting term. A true forecast would require an independent method to predict how the model weights shift over time.
